MSAD_PCA_Walkthrough

### 2017-07-12 LaTeX_Vignette/MS-MVSPC_DissertationVignette.Rnw
Fixed a label

\section{Simulating Data with \texttt{mspProcessData}} \ref{sec:D_DataGen}
This function generates three-dimensional multi-state or single-state non-linear, non-stationary, and autocorrelated process observations. We follow the seminal work of \cite{dong_batch_1996} for generation of the foundational stationary and independent features.

>>>>

\section{Simulating Data with \texttt{mspProcessData}} \label{sec:D_DataGen}
This function generates three-dimensional multi-state or single-state non-linear, non-stationary, and autocorrelated process observations. We follow the seminal work of \cite{dong_batch_1996} for generation of the foundational stationary and independent features.

### 2017-07-12 LaTeX_Vignette/MS-MVSPC_DissertationVignette.tex
Fixed a label

##   Data: num [1:4142, 1:5] 1.062 0.186 0.364 0.335 0.383 ...

@@

##   Data: num [1:4142, 1:7] 2 3 1 1 1 1 1 1 1 1 ...

@@

##  $ Alarms         :An 'xts' object of zero-width

@@

##   .. ..$ SPE_threshold   : Named num 4.61

@@

##   .. ..$ T2_threshold    : Named num 59.6

@@

##   .. ..$ projectionMatrix: num [1:6, 1:2] 0.425 -0.378 0.439 0.434 -0.305 ...
##   .. ..$ LambdaInv       : num [1:2, 1:2] 0.208 0 0 1.482
##   .. ..$ muTrain         : Named num [1:6] 1.39 -2.09 2.99 1.38 -2.05 ...

@@

##   .. ..$ RootPrecisTrain : num [1:6, 1:6] 2.55 0 0 0 0 ...

@@

##   .. ..$ SPE_threshold   : Named num 1.4

@@

##   .. ..$ T2_threshold    : Named num 74.6

@@

##   .. ..$ projectionMatrix: num [1:6, 1:3] -0.4962 -0.0673 0.4888 -0.5234 -0.187 ...
##   .. ..$ LambdaInv       : num [1:3, 1:3] 0.284 0 0 0 0.732 ...
##   .. ..$ muTrain         : Named num [1:6] 3.003 -0.564 -4.526 2.977 -0.589 ...

@@

##   .. ..$ RootPrecisTrain : num [1:6, 1:6] 1.08 0 0 0 0 ...

@@

##   .. ..$ SPE_threshold   : Named num 6.51

@@

##   .. ..$ T2_threshold    : Named num 83.4

@@

##   .. ..$ projectionMatrix: num [1:6, 1:2] -0.393 -0.452 -0.455 0.157 -0.464 ...
##   .. ..$ LambdaInv       : num [1:2, 1:2] 0.274 0 0 0.507
##   .. ..$ muTrain         : Named num [1:6] 0.527 0.273 1.434 0.567 0.259 ...

@@

##   .. ..$ RootPrecisTrain : num [1:6, 1:6] 16.6 0 0 0 0 ...

@@

\subsubsection{Adding Lagged Features}
First, concatenate the last given observation from the training set as ``row 0'' of the test data set. This will enable \texttt{mspMonitor} to include lag-1 features. Similarly, one would include the last $k$ observations of the training set should the process dictate the need for any lag-$k$ features. Because the Fault Start Index was set to 8500, this testing window will show the change point between observations generated under normal conditions and those generated under a fault state.
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlstd{test1A_xts} \hlkwb{<-} \hlstd{fault1A_xts[}\hlnum{8460}\hlopt{:}\hlnum{8520}\hlstd{,} \hlopt{-}\hlnum{1}\hlstd{]}
\hlstd{lagTest1A_xts} \hlkwb{<-} \hlkwd{lag.xts}\hlstd{(test1A_xts,} \hlnum{0}\hlopt{:}\hlnum{1}\hlstd{)}
\hlstd{lagTest1A_xts} \hlkwb{<-} \hlkwd{cbind}\hlstd{(fault1A_xts[}\hlnum{8461}\hlopt{:}\hlnum{8520}\hlstd{,}\hlnum{1}\hlstd{],}
                       \hlstd{lagTest1A_xts[}\hlopt{-}\hlnum{1}\hlstd{,])}
\hlkwd{head}\hlstd{(lagTest1A_xts)}
\end{alltt}
\begin{verbatim}
##                     state         x         y         z       x.1
## 2015-05-22 07:00:00     1 0.5894923 -1.693457 0.9793838 0.4122657
## 2015-05-22 07:01:00     1 0.7076477 -1.693444 1.1569904 0.5894923
## 2015-05-22 07:02:00     1 0.6065543 -1.510750 1.0816650 0.7076477
## 2015-05-22 07:03:00     1 0.5964738 -1.404200 0.9984129 0.6065543
## 2015-05-22 07:04:00     1 0.7359302 -1.492578 0.9049884 0.5964738
## 2015-05-22 07:05:00     1 0.7665503 -1.482806 0.9188497 0.7359302
##                            y.1       z.1
## 2015-05-22 07:00:00  0.1370214 0.4769939
## 2015-05-22 07:01:00 -1.6934574 0.9793838
## 2015-05-22 07:02:00 -1.6934436 1.1569904
## 2015-05-22 07:03:00 -1.5107499 1.0816650
## 2015-05-22 07:04:00 -1.4042005 0.9984129
## 2015-05-22 07:05:00 -1.4925779 0.9049884
\end{verbatim}
\end{kframe}
\end{knitrout}

\subsubsection{Monitoring the Test Data}
With the lagged test observations in the working environment, the \texttt{mspMonitor} function can be applied. This function (similarly to \texttt{mspTrain}) takes in the label information as a separate argument from the input data. Further, the \texttt{mspMonitor} function takes in the \texttt{TrainingSpecs} object returned in the results list from \texttt{mspTrain}. Notice that the first six rows of the monitor matrix are the exact same as the first six rows of the lagged test matrix, except that the rows of the monitor matrix have the monitoring statistic and corresponding indicator columns appended.
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlstd{monitor1A_xts} \hlkwb{<-} \hlkwd{mspMonitor}\hlstd{(}\hlkwc{observations} \hlstd{= lagTest1A_xts[,}\hlopt{-}\hlnum{1}\hlstd{],}
                            \hlkwc{labelVector} \hlstd{= lagTest1A_xts[,}\hlnum{1}\hlstd{],}
                            \hlkwc{trainingSummary} \hlstd{= train1A_ls}\hlopt{$}\hlstd{TrainingSpecs)}
\hlkwd{head}\hlstd{(monitor1A_xts)}
\end{alltt}
\begin{verbatim}
##                             x         y         z       x.1        y.1
## 2015-05-22 07:00:00 0.5894923 -1.693457 0.9793838 0.4122657  0.1370214
## 2015-05-22 07:01:00 0.7076477 -1.693444 1.1569904 0.5894923 -1.6934574
## 2015-05-22 07:02:00 0.6065543 -1.510750 1.0816650 0.7076477 -1.6934436
## 2015-05-22 07:03:00 0.5964738 -1.404200 0.9984129 0.6065543 -1.5107499
## 2015-05-22 07:04:00 0.7359302 -1.492578 0.9049884 0.5964738 -1.4042005
## 2015-05-22 07:05:00 0.7665503 -1.482806 0.9188497 0.7359302 -1.4925779
##                           z.1        SPE SPE_Flag        T2 T2_Flag Alarm
## 2015-05-22 07:00:00 0.4769939 1.23315168        0 28.293817       0    NA
## 2015-05-22 07:01:00 0.9793838 0.06691071        0  3.842885       0    NA
## 2015-05-22 07:02:00 1.1569904 0.43929620        0  4.405378       0    NA
## 2015-05-22 07:03:00 1.0816650 0.86684372        0  5.023986       0    NA
## 2015-05-22 07:04:00 0.9984129 0.45658085        0  4.864228       0    NA
## 2015-05-22 07:05:00 0.9049884 0.74949850        0  4.396364       0    NA
\end{verbatim}
\end{kframe}
\end{knitrout}

>>>>

##   Data: num [1:4142, 1:5] 0.2109 0.0632 0.4924 0.7234 0.6277 ...

@@

##   Data: num [1:4141, 1:7] 2 3 1 1 1 1 1 1 1 1 ...

@@

##  $ Alarms         :An 'xts' object on 2015-05-19 13:13:00/2015-05-19 13:13:00 containing:
##   Data: num [1, 1:11] 1.81 -2.32 4.2 2.07 -2.11 ...
##   ..$ : chr [1:11] "x" "y" "z" "x.1" ...

@@

##   .. ..$ SPE_threshold   : Named num 4.71

@@

##   .. ..$ T2_threshold    : Named num 60.5

@@

##   .. ..$ projectionMatrix: num [1:6, 1:2] 0.423 -0.382 0.437 0.431 -0.315 ...
##   .. ..$ LambdaInv       : num [1:2, 1:2] 0.205 0 0 1.579
##   .. ..$ muTrain         : Named num [1:6] 1.37 -2.1 2.95 1.36 -2.06 ...

@@

##   .. ..$ RootPrecisTrain : num [1:6, 1:6] 2.6 0 0 0 0 ...

@@

##   .. ..$ SPE_threshold   : Named num 1.14

@@

##   .. ..$ T2_threshold    : Named num 76.8

@@

##   .. ..$ projectionMatrix: num [1:6, 1:3] -0.496 -0.065 0.49 -0.523 -0.183 ...
##   .. ..$ LambdaInv       : num [1:3, 1:3] 0.283 0 0 0 0.735 ...
##   .. ..$ muTrain         : Named num [1:6] 2.979 -0.564 -4.508 2.952 -0.589 ...

@@

##   .. ..$ RootPrecisTrain : num [1:6, 1:6] 1.06 0 0 0 0 ...

@@

##   .. ..$ SPE_threshold   : Named num 7.2

@@

##   .. ..$ T2_threshold    : Named num 82.7

@@

##   .. ..$ projectionMatrix: num [1:6, 1:2] -0.393 -0.451 -0.455 0.16 -0.464 ...
##   .. ..$ LambdaInv       : num [1:2, 1:2] 0.278 0 0 0.494
##   .. ..$ muTrain         : Named num [1:6] 0.528 0.27 1.423 0.569 0.256 ...

@@

##   .. ..$ RootPrecisTrain : num [1:6, 1:6] 16.9 0 0 0 0 ...

@@

\subsubsection{Adding Lagged Features}
First, concatenate the last given observation from the training set as ``row 0'' of the test data set. This will enable \texttt{mspMonitor} to include lag-1 features. Similarly, one would include the last $k$ observations of the training set should the process dictate the need for any lag-$k$ features. Because the Fault Start Index was set to 8500, this testing window will show the change point between observations generated under normal conditions and those generated under a fault state.
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlstd{test1A_xts} \hlkwb{<-} \hlstd{fault1A_xts[}\hlnum{8460}\hlopt{:}\hlnum{8520}\hlstd{,} \hlopt{-}\hlnum{1}\hlstd{]}
\hlstd{lagTest1A_xts} \hlkwb{<-} \hlkwd{lag.xts}\hlstd{(test1A_xts,} \hlnum{0}\hlopt{:}\hlnum{1}\hlstd{)}
\hlstd{lagTest1A_xts} \hlkwb{<-} \hlkwd{cbind}\hlstd{(fault1A_xts[}\hlnum{8461}\hlopt{:}\hlnum{8520}\hlstd{,}\hlnum{1}\hlstd{],}
                       \hlstd{lagTest1A_xts[}\hlopt{-}\hlnum{1}\hlstd{,])}
\hlkwd{head}\hlstd{(lagTest1A_xts)}
\end{alltt}
\begin{verbatim}
##                     state         x         y         z       x.1
## 2015-05-22 07:00:00     1 0.6844440 -1.565320 1.1324768 0.3534816
## 2015-05-22 07:01:00     1 0.5454614 -1.369986 0.9184724 0.6844440
## 2015-05-22 07:02:00     1 0.6468377 -1.593779 0.8900444 0.5454614
## 2015-05-22 07:03:00     1 0.3543316 -1.361402 0.7855688 0.6468377
## 2015-05-22 07:04:00     1 0.3831960 -1.455579 0.6319864 0.3543316
## 2015-05-22 07:05:00     1 0.5734844 -1.406738 0.9210589 0.3831960
##                             y.1       z.1
## 2015-05-22 07:00:00  0.08705337 0.4466149
## 2015-05-22 07:01:00 -1.56532037 1.1324768
## 2015-05-22 07:02:00 -1.36998580 0.9184724
## 2015-05-22 07:03:00 -1.59377911 0.8900444
## 2015-05-22 07:04:00 -1.36140249 0.7855688
## 2015-05-22 07:05:00 -1.45557880 0.6319864
\end{verbatim}
\end{kframe}
\end{knitrout}

\subsubsection{Monitoring the Test Data}
With the lagged test observations in the working environment, the \texttt{mspMonitor} function can be applied. This function (similarly to \texttt{mspTrain}) takes in the label information as a separate argument from the input data. Further, the \texttt{mspMonitor} function takes in the \texttt{TrainingSpecs} object returned in the results list from \texttt{mspTrain}. Notice that the first six rows of the monitor matrix are the exact same as the first six rows of the lagged test matrix, except that the rows of the monitor matrix have the monitoring statistic and corresponding indicator columns appended.
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlstd{monitor1A_xts} \hlkwb{<-} \hlkwd{mspMonitor}\hlstd{(}\hlkwc{observations} \hlstd{= lagTest1A_xts[,}\hlopt{-}\hlnum{1}\hlstd{],}
                            \hlkwc{labelVector} \hlstd{= lagTest1A_xts[,}\hlnum{1}\hlstd{],}
                            \hlkwc{trainingSummary} \hlstd{= train1A_ls}\hlopt{$}\hlstd{TrainingSpecs)}
\hlkwd{head}\hlstd{(monitor1A_xts)}
\end{alltt}
\begin{verbatim}
##                             x         y         z       x.1         y.1
## 2015-05-22 07:00:00 0.6844440 -1.565320 1.1324768 0.3534816  0.08705337
## 2015-05-22 07:01:00 0.5454614 -1.369986 0.9184724 0.6844440 -1.56532037
## 2015-05-22 07:02:00 0.6468377 -1.593779 0.8900444 0.5454614 -1.36998580
## 2015-05-22 07:03:00 0.3543316 -1.361402 0.7855688 0.6468377 -1.59377911
## 2015-05-22 07:04:00 0.3831960 -1.455579 0.6319864 0.3543316 -1.36140249
## 2015-05-22 07:05:00 0.5734844 -1.406738 0.9210589 0.3831960 -1.45557880
##                           z.1       SPE SPE_Flag        T2 T2_Flag Alarm
## 2015-05-22 07:00:00 0.4466149 0.2948716        0 28.028452       0    NA
## 2015-05-22 07:01:00 1.1324768 0.9816014        0  5.025385       0    NA
## 2015-05-22 07:02:00 0.9184724 0.0316290        0  4.773963       0    NA
## 2015-05-22 07:03:00 0.8900444 0.8505646        0  6.333569       0    NA
## 2015-05-22 07:04:00 0.7855688 0.2234181        0  6.613971       0    NA
## 2015-05-22 07:05:00 0.6319864 0.4523686        0  5.922610       0    NA
\end{verbatim}
\end{kframe}
\end{knitrout}
